---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oncoPlot  

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/oncoPlot)](https://CRAN.R-project.org/package=oncoPlot)
<!-- badges: end -->  

This package contains functions that plots the Kaplan-Meier Survival Curves 
and Time-to-Treatment histograms as seen at the OHDSI Symposium in September 
2019.

### Requirements  

* Connection details for OMOP CDM version 5. In the examples below, the details 
are in the .Renviron file to ensure connection details remain private in public 
repos. To learn more about this methodology, please visit 
https://csgillespie.github.io/efficientR/3-3-r-startup.html#renviron.  

* R version 3.5.0 or newer. 


## Installation

You can install the development version of oncoPlot from 
[GitHub](https://www.GitHub.com) with:  

```{r}
devtools::install_github("meerapatelmd/oncoPlot")
```  

## Requirements  
* Connection details for OMOP CDM version 5. In the examples below, the details 
are in the .Renviron file to ensure connection details remain private in public 
repos. To learn more about this methodology, please visit 
https://csgillespie.github.io/efficientR/3-3-r-startup.html#renviron.  
* R version 3.5.0 or newer. 

## Example

```{r example}
library(oncoPlot)
```

### Survival Curve  

```{r}
plot_survival(
  dbms = "postgresql", 
  user = Sys.getenv("username"), 
  password = Sys.getenv("password"), 
  server = Sys.getenv("server"), 
  schema = schema, 
  port = port)
```
                        
### Time To Treatment Histogram  

```{r}  
plot_time_to_rx_hist(
  dbms = "postgresql", 
  user = Sys.getenv("username"), 
  password = Sys.getenv("password"), 
  server = Sys.getenv("server"), 
  schema = schema, port = port
  )
```
